---
title: "Overview submitted files"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r load_libraries}
library(tidyverse)
library(gt)
```

```{r ggplot_theme, include = FALSE}
theme_set(theme_bw())
```

# Load data

This analysis is based on Table 3 of the RECCAP2-ocean protocol for model output, and statistics of the ETHZ CESM model output.

```{r Table_3_from_protocol}

# read Table 3 from model protocol
table_3 <- read_csv(
  here::here(
    "data/overview",
    "RECCAP2-ocean_data_products_overview - Model_protocol_table3.csv"
  )
)

# replace placeholder variable name with actual CESM variable name
table_3_temp <- table_3 %>% 
  filter(variable_id == "epc100type / epc1000type") %>% 
  select(-variable_id)

table_3_temp <- expand_grid(
  table_3_temp,
  variable_id = c("epc100hard","epc1000hard","epc100soft","epc1000soft")
)

table_3 <- table_3 %>% 
  filter(variable_id != "epc100type / epc1000type")

table_3 <- bind_rows(table_3, table_3_temp)
rm(table_3_temp)

```


The list of files and sizes of the ETHZ CESM model output refers to the content in this folder:

```{r CESM_output_files_list}

# set path to output
path_ROMS <-
  "/net/kryo/work/loher/ROMS/RECCAP2_Jan2022/SO_d025_global_proto_runA/submit_20220404"
path_ROMS

# create list of CESM output files and sizes

ROMS_files_names <- list.files(path = path_ROMS,
                               pattern = ".nc")
ROMS_files_sizes <-
  file.size(paste(path_ROMS, ROMS_files_names, sep = "/"))

ROMS_files <- bind_cols(file_name = ROMS_files_names,
                        file_size_MB = round(ROMS_files_sizes * 1e-6, 1))

rm(ROMS_files_names, ROMS_files_sizes)

# extract variable_id and experiment_id from file name
ROMS_files <- ROMS_files %>%
  mutate(
    variable_id = str_split(file_name,
                            pattern = "_ROMS",
                            simplify = TRUE)[, 1],
    experiment_id = str_sub(string = file_name, -29, -29)
  ) %>%
  mutate(experiment_id = if_else(
    experiment_id %in% c("A", "B", "C", "D"),
    experiment_id,
    "ancillary"
  )) %>%
  select(-c(file_name))

```

```{r create_overview_table}

# join file list and tab 3
overview <- full_join(table_3, ROMS_files) %>%
  arrange(variable_id) %>% 
  filter(!is.na(file_size_MB))

rm(ROMS_files, table_3)

# write overview file
overview %>%
  write_csv("data/overview/overview_files.csv")

```

# Overview CESM output

Overview table of output files created. Please note, that for each listed variable, `four experiment_id (A-D) versions` exist.

```{r files_list}

overview %>% 
  group_by(variable_id, dimension, priority) %>% 
  summarise_at("file_size_MB", sum, na.rm = TRUE) %>% 
  arrange(dimension, priority) %>% 
  gt(
    rowname_col = "variable_id",
    groupname_col = c("dimension", "priority"),
    row_group.sep = " | Priority: "
  ) %>%
  summary_rows(groups = TRUE,
               fns = list(total = "sum"))

```

## Submission tar files

```{r CESM_submission_files_list}

# create list of CESM output files and sizes

ROMS_files_names_tar <- list.files(path = path_ROMS,
                                   pattern = ".tar")
ROMS_files_sizes_tar <-
  file.size(paste(path_ROMS, ROMS_files_names_tar, sep = "/"))

ROMS_files_tar <- bind_cols(
  file_name = ROMS_files_names_tar,
  file_size_GB = round(ROMS_files_sizes_tar * 1e-9, 1))

rm(path_ROMS, ROMS_files_names_tar, ROMS_files_sizes_tar)

# extract variable_id and experiment_id from file name
ROMS_files_tar


```
