---
title: "Region masks"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}

path_basin_mask <-
  "/nfs/kryo/work/updata/reccap2/"

```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(tidync)
```

# Overview

Three region mask files prepared by Luke Gregor for the analysis within RECCAP2-ocean are available:

1.  `RECCAP2_region_masks_all.nc`
2.  `RECCAP2_openocean_1deg.nc`
3.  `RECCAP2_coastal_MARCAT_1deg.nc`

Please note that the content of 2. an 3. should be identical to the fields `open_ocean` and `coastal_MARCAT` contained in 3. Accordingly, files 2. and 3. are not required for the analysis. In the following, I plot the content of 1.

For the submission, spatially resolved surface fluxes of CO2 should be integrated across the entire `open_ocean` region for `fco2_glob`, and across the indices 1-5 of the `open_ocean` region for `fco2_reg`,

# File: region_masks_all

## Seamask

Please note that the `seamask` provided within 3. is not identical to the `open_ocean` region and should not be used for data analysis.

```{r region_masks_all_seamask}

region_masks_all <-
  read_ncdf(paste(path_basin_mask, "RECCAP2_region_masks_all_v20210412.nc", sep = "")) %>%
  as_tibble()

region_masks_all <- region_masks_all %>%
  mutate(seamask = as.factor(seamask))

region_masks_all %>%
  ggplot(aes(lon, lat, fill = seamask)) +
  geom_raster() +
  coord_quickmap(expand = 0)


```

## Regions

Below, the open ocean regions used to calculate `fgco2_reg` are displayed. Please note that the `coastal_marcats` regions is covered by the other regions.

```{r region_masks_all_regions}

region_masks_all_seamask <- region_masks_all %>%
  select(lat, lon, seamask)

region_masks_all <- region_masks_all %>%
  select(-seamask)

region_masks_all <- region_masks_all %>%
  pivot_longer(open_ocean:southern,
               names_to = "region",
               values_to = "value") %>%
  mutate(value = as.factor(value))

region_masks_all %>%
  filter(value != 0) %>%
  ggplot(aes(lon, lat, fill = region)) +
  geom_raster() +
  scale_fill_brewer(palette = "Dark2") +
  coord_quickmap(expand = 0)


```

## Sub-regions

Each open ocean region consists of several subregions with indices for further regionalization.

```{r region_masks_all_subregions}

region_masks_all %>%
  filter(value != 0) %>%
  group_split(region) %>%
  map(
    ~ ggplot() +
      geom_raster(data = region_masks_all_seamask %>% filter(seamask == 0),
                  aes(lon, lat)) +
      geom_raster(data = .x,
                  aes(lon, lat, fill = value)) +
      coord_quickmap(expand = 0) +
      labs(title = paste("region:", unique(.x$region)))
  )

```

# Write csv file

```{r write_mask_to_csv}

region_masks_all %>% 
  write_csv("data/regions/RECCAP2_region_masks_all_clean.csv")

```


